# (PART) READ QC {-}

# Check Raw Reads Statistics
- Assuming that most QC tools are ready, it is time to use them to do the following:
  - Check the quality of the reads using `fastqc`.
  - Create a summary report of quality metrics using `multiqc`.
  - Trim poor read at a user-specified cutoff using `bbduk.sh`.
  - Remove contaminants `bbduk.sh`.

## Statistics of raw reads
```{r seqkit_raw, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/seqkit_raw.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```


## FastQC on raw reads
```{r fastqc_raw, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/fastqc_raw.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```


![](results/qc/multiqc1/multiqc_plots/svg/mqc_fastqc_per_base_sequence_quality_plot_1.svg)


# Trim Poor Reads

## BBDuk trimming poor reads
```{r bbduk_trim, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/bbduk_trim.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```

## FastQC on trimmed reads
```{r fastqc_trim, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/fastqc_trim.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```

## Seqkit on trimmed reads
```{r seqkit_trim, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/seqkit_trim.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```


![](results/qc/multiqc2/multiqc_plots/svg/mqc_fastqc_per_base_sequence_quality_plot_1.svg)


# Remove Contaminated Reads

## BBDuk read decontamination
```{r bbduk_decontam, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/bbduk_decontam.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```

## FastQC on decontaminated reads
```{r fastqc_decontam, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/fastqc_decontam.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```

## Seqkit on decontaminated reads
```{r seqkit_decontam, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/seqkit_decontam.sh"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```bash\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```




![](results/qc/multiqc3/multiqc_plots/svg/mqc_fastqc_per_base_sequence_quality_plot_1.svg)


# View Processed Read Status


```{r plot_qc_hist, results='asis', echo=FALSE}
# Specify the path to your shell script file
script_path <- "workflow/scripts/plot_qc_hist.R"

# Read the content of the shell script file
script_content <- readLines(script_path)

# Print the content in the R Markdown document
cat("```r\n")
cat(script_content, sep = "\n", collapse = "\n")
cat("\n```")

```

![](images/qc_hist.svg)

